SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Updated the justification of the liveness property (end of Section 5.2)

The satisfaction of the safety property (\ref{eq:FM:safety}) could be
established by applying symbolic model checking techniques.  However,
in this example, it is obvious by inspection of the open automaton.
The satisfaction of the liveness property relies on the observation
that in the state $\ostate{s2,t0}$ only the reset transition involves
$\NameCtrl$.  Therefore, under resonable scheduling assumptions,
$\PortReset$ will always be fired.

>>>>

The satisfaction of the safety property (\ref{eq:FM:safety}) could be
established by applying symbolic model checking techniques.  However,
in this example, it is obvious by inspection of the open automaton.
The satisfaction of the liveness property relies on the observation
that \Simon{the only loop starting in the state $\ostate{s1,t1}$ and involving neither $\mathit{reset}$, nor $\mathit{resume}$ or $\mathit{ask}$, is the self-loop $\mathit{fail(b0)}$.  By further inspecting the synchronisation vector $SV0$, we observe that this self-loop corresponds to the transitions $\mathit{fail(false)}$ and $\mathit{start(false)}$ in the two pLTSs.  Recall that these transitions (carrying the value $\mathit{false}$) are introduced by the encoding. That is, none of the two coordinating components are involved in the joint transition.  Therefore, under resonable scheduling assumptions,
the transition $\mathit{ask}$ will eventually be fired.}
